Non-target amplification

### 2022-03-23 07--nontarget_amplification.Rmd
more filtering which species are used for the comparison

>>>>

## Look for overlap in oomycetes detected

A reviewer requested that we look to see if any oomycetes are detected by ITS1 that are not detected by rps10.

```{r}
obj <- parse_tax_data(abundance_asv, class_cols = 'taxonomy', class_sep = ';',
                      class_regex = '^(.+)--(.+)--(.+)$',
                      class_key = c(taxon = 'taxon_name', boot = 'info', rank = 'taxon_rank'))

# Remove ASVs without confident taxonomic assignments
is_confident_species <- map_lgl(split(obj$data$class_data, obj$data$class_data$input_index), function(x) {
  as.numeric(x$boot[x$rank == "Species"]) >= 50
})
ref_pid <- as.numeric(str_match(obj$data$tax_data$taxonomy, pattern = '--([0-9.]+)--ASV$')[, 2])
obj <- filter_obs(obj, data = "tax_data", is_confident_species & ref_pid > 98, drop_taxa = TRUE)
obj$data$class_data <- NULL

# Remove taxa not in both databases
its_ref <- read_fasta(file.path('intermediate_data', 'reference_databases', 'its1_reference_db.fa'))
rps10_ref <- read_fasta(file.path('intermediate_data', 'reference_databases', 'rps10_reference_db.fa'))
in_both_db <- map_lgl(taxon_names(obj), function(n) {
  any(grepl(names(its_ref), pattern = n, ignore.case = TRUE)) & any(grepl(names(rps10_ref), pattern = n, ignore.case = TRUE))
})
obj <- filter_taxa(obj, in_both_db, supertaxa = TRUE)

# Just look at oomycetes
obj <- filter_taxa(obj, taxon_names == "Oomycetes", supertaxa = FALSE, subtaxa = TRUE)

# Just look at species data
obj <- filter_taxa(obj, taxon_ranks == "Species", supertaxa = FALSE)

# Sum data by taxon
obj$data$tax_abund <- calc_taxon_abund(obj, data = "tax_data", cols = metadata$sample_id, groups = metadata$locus)
obj$data$tax_abund$name <- taxon_names(obj)[obj$data$tax_abund$taxon_id]

# Summarize by locus
obj$data$tax_abund$locus <- "Both"
obj$data$tax_abund$locus[obj$data$tax_abund$rps10 >= minimum_read_count & obj$data$tax_abund$ITS < minimum_read_count] <- 'Rps10'
obj$data$tax_abund$locus[obj$data$tax_abund$rps10 < minimum_read_count & obj$data$tax_abund$ITS >= minimum_read_count] <- 'ITS1'
table(obj$data$tax_abund$locus)
```
